\usepackage[nonumberlist,acronym,numberedsection]{glossaries}

\makenoidxglossaries

\newglossaryentry{Andes lead} {
  name=Andes lead,
  description={A person with a functional understanding of the inner workings of Andes.
   This person has the knowledge and user-rights that permit them to configure a \gls{Mission}, define a \gls{Protocol}, \gls{Sampling Req}, etc.}
}

\newglossaryentry{Bridge} {
  name=Bridge,
  description={
    The Bridge app is meant to be used by a winch operator (normaly a crewmember).
    The operator inputs winch operations (eg.,net/warp deployed/recovered) or actions (eg., net on/off bottom) directly to Andes via the Bridge app.
  }
}

\newglossaryentry{Catch} {
  name=Catch,
  description={
    A table of the Ecosystem Surveys app. A Catch table contains a link to \gls{Set} and \gls{Species} entries, as well as an optional: speciment count, unweighted baskets, relative abundance category and an invertabrate catch ratio.
    Catches can be subdivided into sub-catches having a parent-children relationship.
  }
}

\newglossaryentry{Catch Card} {
  name=Catch Card,
  description={
    Not sure yet, I think it's related to species and how they are measured/detailed
  }
}

\newglossaryentry{CCG} {
  % type=\acronymtype,
  name=CCG,
  description={The Canadian Coast Guard.},
  text={CCG},
  first={Canadian Coast Guard (CCG)}
}

\newglossaryentry{Cruise} {
  name=Cruise,
  description={Same as \gls{Mission}},
}

\newglossaryentry{Current Set} {
  name=Current Set,
  description={
    The \gls{Set} that is currently occuring in time.
    It has begun and is not finished.
    There can only be one \gls{Current Set} at a time.
  },
  see={Set}
}

\newglossaryentry{Closed Set} {
  name=Closed Set,
  description={
    An \gls{Open Set} Can be closed if the data it contains (eg, from \gls{Catch Card}) does not trigger a \gls{Set Flag}.
  },
  see={Set}
}

 \newglossaryentry{Configuration Preset} {
  name=Configuration Preset,
  description={
    Configuration for a particular deployment scenario. Configuration presets include details on the backup locations, and peripherals like GPS, sonars, label printers, etc.
  }
}

\newglossaryentry{Ecosystem Survey} {
  name=Ecosystem Survey,
  description={
    The Ecosystem Survey app is used to as the main data input interface.
    }
}

\newglossaryentry{ESE} {
  % type=\acronymtype,
  name=ESE,
  description={Ecosystem Survey Entry. The ESE replaced \gls{GSE} in the early 2000's.},
  text={ESE},
  first={Ecosystem Survey Entry (ESE)}
}

\newglossaryentry{Fishing Event} {
  name=Fishing Event,
  description={
    An event related to fishing activty of \gls{Set}.
    Metadata such as GPS coordinates and time to are associated with the folllowing event types:
    \emph{net deployed},
    \emph{doors deployed},
    \emph{warp deployed},
    \emph{net on bottom},
    \emph{haul back},
    \emph{net off bottom},
    \emph{door recovered},
    \emph{net recovered},
    and \emph{aborted}.
    A \gls{Set} may contain a list of such event types.
    The Fishing Events are added to the \gls{Set} by a crewmember using the \gls{Bridge} application.
  }
}

\newglossaryentry{GSE} {
  % type=\acronymtype,
  name=GSE,
  description={Groundfish Survey Entry. The GSE is a data entry tool developed in the 1980's.},
  text={GSE},
  first={Groundfish Survey Entry (GSE)}
}

\newglossaryentry{LAN} {
  % type=\acronymtype,
  name=LAN,
  description={Local Area Network},
  text={LAN},
  first={local area network (LAN)}
}

\newglossaryentry{Mission} {
  name=Mission,
  description={
    Same as \gls{Cruise}
  }
}

\newglossaryentry{Open Set} {
  name=Open Set,
  description={
    A \gls{Set} that has not been closed. All new Sets will start in an open state and will remain so untill closed.
    Sets that are activated will automatically be opened.
    The \gls{Current Set} is always open.
  },
  see={Set}
}

\newglossaryentry{ORM} {
  % type=\acronymtype,
  name=ORM,
  description={Object Relational Mapping are an abstraction of relational entities (database tables) as objects.},
  text={ORM},
  first={Object Relational Model (ORM)}
}

\newglossaryentry{Port Sampling} {
  name=Port Sampling,
  description={Scientific program collecting samples from commercial fishing activities.}
}

\newglossaryentry{Protocol} {
  name=Protocol,
  description={TODO}
}

\newglossaryentry{REST-API} {
  name=REST-API,
  description={TODO, just an API over the web yo}
}

\newglossaryentry{Sampling Protocol} {
  name=Sampling Protocol,
  description={The detailed dexcription of what data is to be collected during a scientfic cruise.}
}

\newglossaryentry{Sampling Req} {
  name=Sampling Requirements,
  description={The species-specific requirements for samples to be collected during a scientific cruise.}
}

\newglossaryentry{Set} {
  name=Set,
  description={
    A Set contains all fishing activity and sampling results for a particular \gls{Station}.
  }
}

\newglossaryentry{Set Flag} {
  name=Set Flag,
  description={A flag used to indicate that the data contained within the set has failed to pass a specific validation tests.
  Closing an \gls{Open Set} with active flags can be done by overriding the validation mechanism},
  see=\gls{Set}
  }

\newglossaryentry{Station} {
  name=Station,
  description={A target location specificied by coordinates where a scientific activity is to take place. }
}

\newglossaryentry{Species} {
  name=Species,
  description={An identifiable taxon that can be assigned to a species code.}
}

\newglossaryentry{VBA} {
  % type=\acronymtype,
  name=VBA,
  description={Visual Basic for Applications},
  text={VBA},
  first={Visual Basic for Applications (VBA)}
}

\glsaddall
\glsaddallunused
